---
title: "Example Pretty XTable"
author: "Keaton Stagaman"
date: "July 7, 2016"
output: 
    pdf_document:
        includes:
            in_header: header2.tex
        keep_tex: true
---

## Load libraries and source files

```{r libraries_and_sources, message=FALSE}
library(qdap)
library(ggfortify)
library(ggplot2)
theme_set(theme_bw())
source("../xtable_summary.R")
```

## Data plot with regression line

```{r mtcars_plot, fig.width=6, fig.heigh=3.5, fig.cap="Car distance by speed with regression line"}
ggplot(mtcars, aes(x=disp, y=mpg)) + 
    geom_point(aes(color=as.factor(cyl)), size=3) + 
    scale_color_brewer(name="Cylinders", palette="Accent") + 
    stat_smooth(method="lm") + 
    labs(x="Displacement", y="Miles per Gallon")
```


## Linear model calculation

```{r mtcars_lm}
mtcars.lm <- lm(mpg ~ disp*cyl, data=mtcars)
xtable.summary(model.obj=mtcars.lm, 
               file.id="mtcars", 
               alt.factor.names=mgsub(c("disp", "cyl"), 
                                      c("Displacement", "Cylinders"), 
                                      attributes(mtcars.lm$terms)$term.labels))
```

\begin{table}[h!]
\captionsetup[subtable]{labelformat=empty}
\centering
\subfloat[]{\label{tab:mtcars_lm-a}{\input{mtcars_lm_factors}}}\quad
\subfloat[]{\label{tab:mtcars_lm-b}{\input{mtcars_lm_rsqP}}}
\caption{Linear model for Miles per Gallon by Displacement and Number of Cylinders}
\label{tab:mtcars_lm}
\end{table}

## Factor analysis

```{r mtcars_factanal}
factanal1 <- factanal(mtcars, factors=1, scores="regression")
paste("1 factor p-val:", factanal1$PVAL)
factanal2 <- factanal(mtcars, factors=2, scores="regression")
paste("2 factor p-val:", factanal2$PVAL)
factanal3 <- factanal(mtcars, factors=3, scores="regression")
paste("3 factor p-val:", factanal3$PVAL)
xtable.summary(model.obj=factanal3, 
               file.id="mtcars", 
               cutoff=0.4, 
               alt.factor.names=c("Miles/Gal", 
                                  "No. Cylinders", 
                                  "Displacement", 
                                  "Horsepower", 
                                  "Rear Axle Ratio", 
                                  "Weight", 
                                  "1/4 mile time", 
                                  "V/S", 
                                  "Transmission", 
                                  "No. Fwd Gears", 
                                  "No. Carburetors"))
```

\begin{table}[h!]
\captionsetup[subtable]{labelformat=empty}
\centering
\subfloat[]{\label{tab:mtcars_fa-a}{\input{mtcars_factanal_uniq}}}\quad
\subfloat[]{\label{tab:mtcars_fa-b}{\input{mtcars_factanal_loadings}}}\quad
\subfloat[]{\label{tab:mtcars_fa-c}{\input{mtcars_factanal_vars}}}
\caption{Factor analysis results}
\label{tab:mtcars_fa}
\end{table}

## Model Selection

```{r}
m0 <- lm(mpg ~ cyl, data=mtcars)
m1 <- lm(mpg ~ cyl + disp, data=mtcars)
m2 <- lm(mpg ~ cyl + disp + hp, data=mtcars)
m3 <- lm(mpg ~ cyl + disp + hp + drat, data=mtcars)
m4 <- lm(mpg ~ cyl + disp + hp + drat + wt, data=mtcars)
mtcars.anova <- anova(m0, m1, m2, m3, m4)
xtable.summary(model.obj=mtcars.anova, 
               file.id="mtcars",
               alt.models.text=mgsub(c("mpg", "cyl", "disp", "hp", "drat", "wt"),
                                     c("Miles/Gal",
                                       "No. Cylinders",
                                       "Displacement",
                                       "Horsepower",
                                       "Rear Axle Ratio",
                                       "Weight"),
                                     attributes(mtcars.anova)$heading[2],
                                     trim=FALSE))
```

\begin{table}[h!]
\captionsetup[subtable]{labelformat=empty}
\centering
\subfloat[]{\label{tab:mtcars_anova-a}{\input{mtcars_anovaHeading}}}\quad
\subfloat[]{\label{tab:mtcars_anova-b}{\input{mtcars_anova}}}
\caption{Model Selection for Factors Contributing to Miles per Gallon}
\label{tab:mtcars_anova}
\end{table}
